Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-06 manuscript.Rmd
Compute march_inaug

travel_time_sf <- travel_time_sf %>%
  mutate(distance = st_distance(centroids, mnm_sf$geometry, by_element = TRUE)) %>%
  mutate(march_inaug = 0)

travel_time_sf[11122:11676, "march_inaug"] = 1
#entries 11122 to 11676
```

@@

Queen <- as.nb.sgbp(st_queen(week_1))
W <- nb2mat(Queen, style='B', zero.policy = TRUE)

plot(week_1["mean_travel_time"])
plot(Queen, week_1$centroids, col="blue", cex = 0.5, lwd = 0.5)
```

>>>>

travel_time_sf <- travel_time_sf %>%
  mutate(distance = st_distance(centroids, mnm_sf$geometry, by_element = TRUE)) %>%
  mutate(ifelse((year == 2017 && month == 1 && week %in% c(3, 4)), 1, 0))

# travel_time_sf[11122:11676, "march_inaug"] = 1
#entries 11122 to 11676
```

@@

Queen <- as.nb.sgbp(st_queen(weeks34))
W <- nb2mat(Queen, style='B', zero.policy = TRUE)

plot(weeks34["mean_travel_time"])
plot(Queen, weekw34$centroids, col="blue", cex = 0.5, lwd = 0.5)
```
